Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2012-11-16 doc/references.tex
more draft editing
replace accidentally deleted files

\bibitem[LSST Science Collaboration et al.(2009)]{LSST} LSST 
Science Collaboration, Abell, P.~A., Allison, J., et al.\ 2009, 
arXiv:0912.0201

@@

>>>>

\bibitem[LSST Science Collaboration (2009)]{LSST} LSST 
Science Collaboration: Abell, P.~A., Allison, J., et al.\ 2009, 
arXiv:0912.0201

@@

\bibitem[Semboloni et al.(2012)]{Semboloni+2012} Semboloni, E., 
Hoekstra, H., \& Schaye, J.\ 2012, arXiv:1210.7303
